Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-02-29 main_paper.tex
Revise description of 2nd algorithm

CCT solve this problem by deriving the analytical form of the first-order bias
and explicitly recentering $\hat\tau(h)$. Under weaker assumptions on the
asymptotic behavior of the bandwidth, which we will specify in
Assumption~\ref{A2}, CCT show that the approximate bias of $\hat\tau(h)$ has the
form
\begin{equation*}
  \E(\hat{\tau}(h) \mid \chi_{n}) - \tau =
  h^{2}\Big[ \tfrac{\mu_{+}^{(2)}}{2}\Bf_{+}(h)
  - \tfrac{\mu_{-}^{(2)}}{2}\Bf_{-}(h) \Big]
  (1+o_{p}(1))
\end{equation*}
where $\Bf_{+}(h)$ and $\Bf_{-}(h)$ are observed quantities that depend on the
kernel, bandwidth, and running variables $X_1,\dots,X_n$; formal definitions of
these terms are given in the Mathematical Appendix as Equations~\eqref{eq:3}
and~\eqref{eq:4}. The plug-in bias-corrected estimator then requires estimates
for the second derivatives of the conditional mean from above and below the
cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$, and CCT show that these derivatives
can be estimated by fitting a second order local polynomial, i.e. one order
higher than the polynomial used to obtain $\hat{\tau}$, using a (potentially)
different pilot bandwidth $b$. Their procedure gives the bias-corrected
estimator
\begin{gather*}
  \hat{\tau}'(h, b) = \hat{\tau}(h) - h^{2}
  \Big[\tfrac{\hat{\mu}_{+}^{(2)}(b)}{2} \Bf_{+}(h)
  - \tfrac{\hat{\mu}_{-}^{(2)}(b)}{2}\Bf_{-}(h) \Big]
\end{gather*}
The variance introduced by the bias-correction term does not vanish, so the
naive confidence interval needs not only to be re-centered to correct the bias,
but also rescaled to allow for the additional variability introduced by the bias
correction, resulting in the following asymptotic approximation:
\begin{equation*}
  T'(h, b) = \frac{\hat{\tau}'(h, b) - \tau}{V'(h, b)^{1/2}}
  \to^d N(0,1)
\end{equation*}
with $V'(h, b) = V(h) + C(h, b)$ and $C(h, b)$ an additional variance component
generated by the bias-correction term. This new approximation can be used
instead of~\eqref{eq:1} to construct ``bandwidth robust'' confidence intervals,
and CCT provide simulation evidence that their intervals perform well in finite
samples.

@@

Building upon the results and intuition developed by CCT we propose to implement a first-order bias correction and obtain valid CIs through a bootstrap procedure.
Intuitively, for the local-linear RD estimator's case, we will rely on a local quadratic polynomial approximation for the conditional outcome around the cutoff to capture the potential bias present in the original RD estimate. This insight comes directly from CCT's results using the same local quadratic approximation to estimate bias term as presented in Section \ref{background}.

The first algorithm describes how to obtain a point estimate and perform the bias correction. The second algorithm obtains its confidence interval with correct coverage. For simplicity, we adopt the same optimal-AMSE bandwidth selector proposed by CCT.\footnote{An interesting question is whether one could use a bootstrap based procedure to select a bandwidth that would achieve similar (or improved) results. This is beyond the scope of this particular paper but is part of ongoing research effort.}

Essentially, we apply CCT's insight that a polynomial one order higher can capture the first-order bias behavior and create a bootstrap procedure that can correctly mimic the behavior of the bias present in the original estimator. For such, for a chosen bandwidth, we estimate a local quadratic regression as suggested by CCT, but then bootstrap data by imposing the local quadratic functional form as the DGP. Then, in the bootstrap data the DGP is known. Let the ``true'' treatment effect under the bootstrap DGP be denoted by $\tau^{*}$. We then estimate the treatment effect using the (misspecified) local linear estimator, $\hat{\tau}^{*}$ to the generated data. Hence, the bias for a specific bootstrap data is given by $\tau^{*}-\hat{\tau}^{*}$. More importantly, by generating new bootstrapped data based on the same quadratic DGP and its residual's distribution, we can obtain an estimate of the first-order bias (the part that is captured by $\hat{\Bs}(h,b)$ in CCT's formulas on Section \ref{background}) in the original estimate by averaging across the bias in all $B$ bootstrapped data estimates, i.e., $\tau^{*} - \sum_{i = 1}^{B} \hat{\tau}_{ i}^{*}$. Algorithm~\ref{Alg1} describes this procedure step-by-step for clarity.

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h$ and $b$ are bandwidths as defined by Assumption~\ref{A2} and define
  \begin{align*}
    I_-(h) &= \{i : -h < X_{i} < 0\}, &
    I_+(h) &= \{i : 0 \leq X_{i} < h\}.
  \end{align*}
  Also define $M_-(h)$ and $M_+(h)$ to be the number of elements in $I_-(h)$ and
  $I_+(h)$ respectively and $m_-(h,1),\dots,m_-(h,M_-(h))$ and
  $m_+(h,1),\dots,m_+(h,M_+(h))$ to be subsequences of $1,\dots,n$ that index
  $I_-(h)$ and $I_+(h)$ respectively.
  \begin{enumerate}
  \item Estimate local second order polynomials $\hat g_-$ and $\hat g_+$ using
    the observations in $I_-(b)$ and $I_+(b)$:
    \begin{align*}
      \hat g_-(x)
      &= \hat\beta_{-,0} + \hat\beta_{-,1} x + \hat\beta_{-,2} x^2,
      &\hat g_+(x)
      &= \hat\beta_{+,0} + \hat\beta_{+,1} x + \hat\beta_{+,2} x^2
    \end{align*}
    with
    \begin{align*}
      \hat\beta_- &= \argmin_\beta \sum_{i \in I_-(b)}
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^2 \\
      \hat\beta_+ &= \argmin_\beta \sum_{i \in I_+(b)}
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^2.
    \end{align*}
    Calculate the residuals
    \begin{equation*}
      \hat\varepsilon_{i} =
      \begin{cases}
        Y_{i} - \hat g_-(X_{i}) & \textif\ X_{i} < 0 \\
        Y_{i} - \hat g_+(X_{i}) & \otherwise
      \end{cases}
    \end{equation*}
  \item Repeat the following steps $B_1$ times to produce a sequence of
    bootstrap estimates $\hat\tau_1^*(h),\dots,\hat\tau_{B_1}^*(h)$. For the
    $k$th estimate:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M_-(b)$ from
      $\{\hat\varepsilon_i : i \in I_-(b)\}$ and one of size $M_+(b)$ from
      $\{\hat\varepsilon_i : i \in I_+(h)\}$. Let $\varepsilon_{-,i}^{*}$ and
      $\varepsilon_{+,i}^{*}$ denote the $i$th element of each sample and
      construct
      \begin{align*}
        Y_{-,m_-(h,i)}^* &= \hat g_-(X_{m_-(h,i)}) + \varepsilon_{-,i}^{*} &
        Y_{+,m_+(h,i)}^* &= \hat g_+(X_{m_-(h,i)}) + \varepsilon_{+,i}^{*}.
      \end{align*}
    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
      local linear model on the bootstrap data set:\footnote{%
        Note that the indices of summation are chosen to correspond to the
        indices of the variables generated in the previous step.} %
      \begin{align*}
        \hat\mu_-^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[-]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2 \\
        \hat\mu_+^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[+]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2.
      \end{align*}
    \item Save $\hat\mu_+^*(h) - \hat\mu_-^*(h)$ as $\hat\tau^*_k$.
    \end{enumerate}
  \item Estimate the bias as
    \begin{equation*}
      \Delta^*(h,b) = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
      \big[\hat g_+(0) - \hat g_-(0)\big].
    \end{equation*}
  \end{enumerate}
\end{algorithm}

Under Assumptions~\ref{A1} and~\ref{A2} the procedure described by
Algorithm~\ref{Alg1} provides a consistent estimator of the bias component that
converges fast enough in probability that it can be be used as a correction. As
is standard in the bootstrap literature, we will assume that the number of
bootstrap replications, $B_{1}$, is large enough that the simulation error can
be ignored.

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1} and~\ref{A2},
\begin{equation}
  \label{eq:2}
  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V(h, b)^{1/2}}
  \to^{d} N(0,1)
\end{equation}
\end{theorem}

Note that the variance component of~\eqref{eq:2} is the same value used by CCT
and introduced in~\eqref{eq:1}. Theorem~\ref{T1} implies that our
bias-corrected estimator has the same asymptotic distribution as CCT's. This
equivalence should be unsurprising; both estimators use a 2nd order polynomial
to directly estimate the bias of the local linear model, so they should behave
very similarly.

With Algorithm~\ref{Alg1} at hand, we can move to generate the bias-corrected confidence intervals to perform inference about $\tau$. Here the idea is similar, but now we actually calculate a bias corrected estimate using Algorithm~\ref{Alg1} for every bootstrapped dataset generated, a bootstrap within the bootstrap. Each one of the bias corrected estimates for the generated data is denoted $\hat{\tau}^{bc*}$. These estimator's empirical distribution capture the variability induced by the first order bias correction that lead CCT to propose the rescaling of their confidence intervals by introducing $C^{bc}(h,b)$ in the asymptotic variance formula on Section \ref{background}.

\begin{algorithm}[Confidence intervals]\label{Alg2}
  Define $I_-$, $I_+$, $M_-$, and $M_+$ as in Algorithm~\ref{Alg1}.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^{+}$ and $g_{p+1}^{-}$ as defined by
    Equation --- and define the residuals
    \begin{equation*}
      \hat\varepsilon_{i} =
      \begin{cases}
        Y_i - \hat g_{p+1}^-(X_{i}) & \textif\ X_{i} < 0 \\
        Y_i - \hat g_{p+1}^+(X_{i}) & \otherwise
      \end{cases}
    \end{equation*}
  \item Repeat the following steps $B_{2}$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^{\prime*},\dots,\hat\tau_{B_{2}}^{\prime*}$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M_-(b)$ from
      $\{\hat\varepsilon_{i} : i \in I_-(b)\}$ and one of size $M_+(b)$ from
      $\{\hat\varepsilon_i : i \in I_+(h)\}$. Let $\varepsilon_{i}^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align*}
        Y_{-,i}^* &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_{+,i}^* &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align*}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align*}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M_-(h)} (Y_{-,i}^* -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M_+(h)} (Y_{+,i}^* -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
      \end{align*}
    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set,
      \begin{equation*}
        (Y_1^{*-}, X_1^{*-}),\dots,(Y_{M_-(b)}^{*-},X_{M_-(b)}^{*-}),
        (Y_1^{*+}, X_1^{*+}),\dots,(Y_{M_+(b)}^{*+},X_{M_+(b)}^{*+}),
      \end{equation*}
      using the same bandwidths $h$ and $b$ that are used in the rest of
      this algorithm but reestimating all of the local polynomials on the
      bootstrap data. Let $\Delta^{**}$ represent the bias estimator returned
      by Algorithm~\ref{Alg1}.
    \item Save the bias-corrected estimator
      $\hat\tau_k^{\prime*} = \hat\mu_+^* - \hat\mu_i^* - \Delta^{**}$.
    \end{enumerate}
  \item Define the confidence interval endpoints $\hat\ell(\alpha)$ and
    $\hat u(\alpha)$ as the $\alpha/2$ and $1-\alpha/2$ quantiles of the
    empirical CDF of $\hat\tau_1^{\prime*},\dots,\hat\tau_{B_2}^{\prime*}$.
  \end{enumerate}
\end{algorithm}

As earlier, we assume that $B_1$ and $B_2$ are large enough that simulation
error can be ignored. Define the limiting values
\begin{align*}
\Delta^{**} &= \plim_{B_1,B_2 \to \infty} \Delta^{**}_{B_1,B_2} \\
\hat\ell^*(\alpha) &= \plim_{B_1,B_2 \to \infty} \hat\ell^*_{B_1,B_2}(\alpha) \\
\hat u^*(\alpha) &= \plim_{B_1,B_2 \to \infty} \hat u^*_{B_1,B_2}(\alpha).
\end{align*}

Theorem~\ref{T2} establishes that this ``bootstrap-within-bootstrap''
approximates the asymptotic distribution of the bias-corrected
statistic proposed by Algorithm~\ref{Alg1} and justifies this second
algorithm.

\begin{theorem}\label{T2}
  Under Assumptions~\ref{A1} and~\ref{A2},
  \begin{gather*}
    \V^*(\hat\tau^{*} - \Delta^{**})/V(h,b) \to^p 1
  \intertext{and}
    \sup_{x}
    \Big\rvert \Pr^*[\hat\tau^{*} - \Delta^{**} - \tau^* \leq x ]
    - \Pr[\hat\tau - \Delta^* - \tau \leq x] \Big\lvert \to^p 0.
  \end{gather*}
\end{theorem}

@@

Define the following additional notation:
$r_p(x) = (1,\ x,\dots,\ x^p)'$,
\begin{align}
  \label{eq:3}
  \Bf_+(h)
  & = (1\ \  0)\ \Big(\ssum[+]{i}{h} r_1(X_i/h) r_1(X_i/h)' \Big)^{-1}
    \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
  \label{eq:4}
  \Bf_-(h)
  & = (1\ \ 0)\ \Big(\ssum[-]{i}{h} r_1(X_i/h) r_1(X_i/h)' \Big)^{-1}
    \ssum[-]{i}{h} r_1(X_i/h) \; X_i^2 / h^2.
\end{align}

\subsection{Proof of Theorem~\ref{T1}}
We have
\begin{equation*}
  \hat\tau(h) - \Delta^*(h,b) - \tau = (\hat\tau(h) - \E \hat \tau(h)) +
  (\E \hat \tau(h) - \tau) - (\E^* \hat \tau^*(h) - \tau^*).
\end{equation*}
The design of the bootstrap ensures that
\begin{align*}
  \E^* \hat\mu_{+}^*(h) - \mu_{+}^{*}
  &= h^{2} \mu_+^{*(2)} \Bf_{+}(h)/2,
  &\E^* \hat\mu_{-}^*(h) - \mu_{-}^{*}
  &= h^{2} \mu_-^{*(2)} \Bf_{-}(h)/2,
\end{align*}
almost surely, implying that
\begin{equation*}
    \E^* \hat\tau^*(h) - \tau^{*} = h^2\, \mu_+^{*(2)} \Bf_+(h)/2
      - h^2\, \mu_{-}^{*(2)} \Bf_{-}(h)/2.
\end{equation*}
Combining this result with CCT's Lemma A1, gives
\begin{align}
  \hat\tau(h) - & \E \hat\tau(h) + (\E \hat\tau(h) - \tau) - (\E^* \hat\tau^*(h) - \tau^*)\notag \\
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h) / 2 \big) + O_p(h^{3}) \notag \\
  \label{eq:5}
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 (\hat\mu_-^{(2)}(b) - \mu_-^{(2)}) \Bf_{-}(h) /2 \\
  \notag
  &\pushright{- h^2 (\hat\mu_+^{(2)}(b) - \mu_+^{(2)}) \Bf_{+}(h) / 2 + O_p(h^{3})}
\end{align}
The second equality holds because
$\mu_+^{*(2)} = \hat\mu_{+}^{(2)}(b)$ and
$\mu_-^{*(2)} = \hat\mu_{-}^{(2)}(b)$ almost surely. Asymptotic
normality then follows from normality of $\hat\tau(h) - \E\hat\tau(h)$,
$\hat\mu_+^{(2)}(b) - \mu_+^{(2)}$, and
$\hat\mu_-^{(2)}(b) - \mu_-^{(2)}$ using similar arguments to
CCT's Lemma SA4.D.\qed

>>>>

CCT solve this problem by deriving the analytical form of the first-order bias
and explicitly recentering $\hat\tau(h)$. Under weaker assumptions on the
asymptotic behavior of the bandwidth, which we will specify in
Assumption~\ref{A2}, CCT show that the approximate bias of $\hat\tau(h)$ has the
form
\begin{equation*}
  \E(\hat{\tau}(h) \mid \chi_{n}) - \tau =
  h^{2}\Big[ \tfrac{\mu_{+}^{(2)}}{2}\Bf_{+}(h)
  - \tfrac{\mu_{-}^{(2)}}{2}\Bf_{-}(h) \Big]
  (1+o_{p}(1))
\end{equation*}
where $\Bf_{+}(h)$ and $\Bf_{-}(h)$ are observed quantities that depend on the
kernel, bandwidth, and running variables $X_1,\dots,X_n$; formal definitions of
these terms are given in the Mathematical Appendix as Equations~\eqref{eq:5}
and~\eqref{eq:6}. The plug-in bias-corrected estimator then requires estimates
for the second derivatives of the conditional mean from above and below the
cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$, and CCT show that these derivatives
can be estimated by fitting a second order local polynomial, i.e. one order
higher than the polynomial used to obtain $\hat{\tau}$, using a (potentially)
different pilot bandwidth $b$. Their procedure gives the bias-corrected
estimator
\begin{gather*}
  \hat{\tau}'(h, b) = \hat{\tau}(h) - h^{2}
  \Big[\tfrac{\hat{\mu}_{+}^{(2)}(b)}{2} \Bf_{+}(h)
  - \tfrac{\hat{\mu}_{-}^{(2)}(b)}{2}\Bf_{-}(h) \Big]
\end{gather*}
The variance introduced by the bias-correction term does not vanish, so the
naive confidence interval needs not only to be re-centered to correct the bias,
but also rescaled to allow for the additional variability introduced by the bias
correction, resulting in the following asymptotic approximation:
\begin{equation*}
  T'(h, b) = \frac{\hat{\tau}'(h, b) - \tau}{V'(h, b)^{1/2}}
  \to^d N(0,1)
\end{equation*}
with $V'(h, b) = V(h) + C(h, b)$ and $C(h, b)$ an additional variance component
generated by the bias-correction term. This new approximation can be used
instead of~\eqref{eq:1} to construct ``bandwidth robust'' confidence intervals,
and CCT provide simulation evidence that their intervals perform well in finite
samples.

@@

This section presents our theoretical contributions. We propose two algorithms
in this section. The first uses a residual bootstrap based on based on a second
order local polynomial to estimate the bias of the local linear model. That
estimate can be subtracted from the biased original estimator to provide an
asymptotically unbiased estimator with the same asymptotic distribution as
CCT's. As in CCT, this bias correction term introduces a new source of variance,
invalidating standard (naive) critical values. Consequently, the second
algorithm we propose uses an iterated bootstrap to estimate the correct
critical values of the bias corrected estimator.

The intuition behind both procedures is very straightforward. CCT show that a
local second order polynomial captures all of the unmodeled aspects of the DGP
necessary for constructing valid confidence intervals. Our proposed algorithms
estimate and embed the second order behavior in the bootstrap DGP through
a residual bootstap.
Algorithm~\ref{Alg1} explains the bias-correction steps in detail.

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h$ and $b$ are bandwidths as defined by Assumption~\ref{A2} and define
  \begin{align*}
    I_-(h) &= \{i : -h < X_{i} < 0\}, &
    I_+(h) &= \{i : 0 \leq X_{i} < h\}.
  \end{align*}
  Also define $M_-(h)$ and $M_+(h)$ to be the number of elements in $I_-(h)$ and
  $I_+(h)$ respectively and $m_-(h,1),\dots,m_-(h,M_-(h))$ and
  $m_+(h,1),\dots,m_+(h,M_+(h))$ to be subsequences of $1,\dots,n$ that index
  $I_-(h)$ and $I_+(h)$ respectively.
  \begin{enumerate}
  \item Estimate local second order polynomials $\hat g_-$ and $\hat g_+$ using
    the observations in $I_-(b)$ and $I_+(b)$:
    \begin{align}
      \label{eq:2}
      \hat g_-(x)
      &= \hat\beta_{-,0} + \hat\beta_{-,1} x + \hat\beta_{-,2} x^2,
      &\hat g_+(x)
      &= \hat\beta_{+,0} + \hat\beta_{+,1} x + \hat\beta_{+,2} x^2
    \end{align}
    with
    \begin{align*}
      \hat\beta_- &= \argmin_\beta \sum_{i \in I_-(b)}
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^2 \\
      \hat\beta_+ &= \argmin_\beta \sum_{i \in I_+(b)}
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^2.
    \end{align*}
    Calculate the residuals
    \begin{equation}
      \label{eq:3}
      \hat\varepsilon_{i} =
      \begin{cases}
        Y_{i} - \hat g_-(X_{i}) & \textif\ X_{i} < 0 \\
        Y_{i} - \hat g_+(X_{i}) & \otherwise.
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_1$ times to produce a sequence of
    bootstrap estimates $\hat\tau_1^*(h),\dots,\hat\tau_{B_1}^*(h)$. For the
    $k$th estimate:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M_-(b)$ from
      $\{\hat\varepsilon_i : i \in I_-(b)\}$ and one of size $M_+(b)$ from
      $\{\hat\varepsilon_i : i \in I_+(h)\}$. Let $\varepsilon_{-,i}^{*}$ and
      $\varepsilon_{+,i}^{*}$ denote the $i$th element of each sample and
      construct
      \begin{align*}
        Y_{-,m_-(h,i)}^* &= \hat g_-(X_{m_-(h,i)}) + \varepsilon_{-,i}^{*} &
        Y_{+,m_+(h,i)}^* &= \hat g_+(X_{m_-(h,i)}) + \varepsilon_{+,i}^{*}.
      \end{align*}
    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
      local linear model on the bootstrap data set:\footnote{%
        Note that the indices of summation are chosen to correspond to the
        indices of the variables generated in the previous step.} %
      \begin{align*}
        \hat\mu_-^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[-]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2 \\
        \hat\mu_+^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[+]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2.
      \end{align*}
    \item Save $\hat\tau^*_k(h) = \hat\mu_+^*(h) - \hat\mu_-^*(h)$.
    \end{enumerate}
  \item Estimate the bias as
    \begin{equation*}
      \Delta^*(h,b) = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
      \big[\hat g_+(0) - \hat g_-(0)\big].
    \end{equation*}
  \end{enumerate}
\end{algorithm}
Note that $\hat g_+(0) - \hat g_-(0)$ is the true treatment effect under the
distribution induced by this bootstrap. The bootstrap estimator works by
constructing an approximate DGP with known properties. As the dataset gets
larger, the approximate DGP mimics the unknown real DGP more closely, and the
population parameter values in the bootstrap DGP can become accurate estimates
of the true parameter values in the real DGP.

Under Assumptions~\ref{A1} and~\ref{A2} the procedure described by
Algorithm~\ref{Alg1} provides a consistent estimator of the bias component that
converges fast enough in probability that it can be be used as a correction. As
is standard in the bootstrap literature, we will assume that the number of
bootstrap replications, $B_{1}$, is large enough that the simulation error can
be ignored. Theorem~\ref{T1} presents the result formally.

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1} and~\ref{A2},
\begin{equation}
  \label{eq:4}
  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V'(h, b)^{1/2}}
  \to^{d} N(0,1)
\end{equation}
\end{theorem}

Note that the variance component of~\eqref{eq:4} is the same value used by CCT
and introduced in~\eqref{eq:1}. Theorem~\ref{T1} implies that our bias-corrected
estimator has the same asymptotic distribution as CCT's. This equivalence should
be unsurprising; both estimators use a 2nd order polynomial to directly estimate
the bias of the local linear model, so they should behave very similarly.

Since the second order polynomial captures the relevant aspects of the DGP for
estimating the variance as well as the bias, the asymptotic distribution of the
bias corrected estimator $\hat\tau(h) - \Delta^*(h,b)$ can also be approximated
with a bootstrap. We propose bootstrapping $\hat\tau(h) - \Delta^*(h,b)$ using
the same residual bootstrap method that was used in
Algorithm~\ref{Alg1}. Algorithm~\ref{Alg2} provides the details of our procedure
and Theorem~\ref{T2} establishes its theoretical properties.

\begin{algorithm}[Confidence intervals]\label{Alg2}
  Define the same notation as in Algorithm~\ref{Alg1}.
  \begin{enumerate}
  \item Estimate $\hat g_+$ and $g_-$ and generate the residuals
    $\hat\varepsilon_i$ just as in Algorithm~\ref{Alg1}; Equations~\eqref{eq:2}
    and~\eqref{eq:3}.
  \item Repeat the following steps $B_{2}$ times to produce a sequence of
    bootstrap estimates
    $\hat\tau_1^{\prime*}(h,b), \dots, \hat\tau_{B_{2}}^{\prime*}(h,b)$. For the
    $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M_-(b)$ from
      $\{\hat\varepsilon_i : i \in I_-(b)\}$ and one of size $M_+(b)$ from
      $\{\hat\varepsilon_i : i \in I_+(h)\}$. Let $\varepsilon_{-,i}^{*}$ and
      $\varepsilon_{+,i}^{*}$ denote the $i$th element of each sample and
      construct
      \begin{align*}
        Y_{-,m_-(h,i)}^* &= \hat g_-(X_{m_-(h,i)}) + \varepsilon_{-,i}^{*} &
        Y_{+,m_+(h,i)}^* &= \hat g_+(X_{m_-(h,i)}) + \varepsilon_{+,i}^{*}.
      \end{align*}
    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
      local linear model on the bootstrap data set:
      \begin{align*}
        \hat\mu_-^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[-]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2 \\
        \hat\mu_+^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[+]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2.
      \end{align*}
    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set,
      \begin{multline*}
        (Y_{-,m_-(b,1)}^{*}, X_{-,m_-(b,1)}),\dots,
        (Y_{-,m_-(b,M_-(b))}^{*},X_{-,m_-(b,M_-(b))}), \\
        (Y_{+,m_+(b,1)}^{*}, X_{+,m_+(b,1)}),\dots,
        (Y_{+,m_+(b,M_+(b))}^{*},X_{+,m_+(b,M_+(b))})
      \end{multline*}
      using the same bandwidths $h$ and $b$ that are used in the rest of this
      algorithm but reestimating all of the local polynomials on the bootstrap
      data. Generate $B_1$ new bootstrap samples and let $\Delta^{**}(h,b)$
      represent the bias estimator returned by Algorithm~\ref{Alg1}.
    \item Save the bias-corrected estimator
      $\hat\tau_k^{\prime*}(h,b) = \hat\mu_+^*(h) - \hat\mu_i^*(h)
      - \Delta^{**}(h,b)$.
    \end{enumerate}
  \item Use the empirical CDF of
    $\hat\tau_1^{\prime*}(h,b),\dots \hat\tau_{B_2}^{\prime*}(h,b)$ to
    construct confidence intervals, etc.
  \end{enumerate}
\end{algorithm}

Theorem~\ref{T2} establishes that this iterated bootstrap approximates the
asymptotic distribution of the bias-corrected statistic proposed by
Algorithm~\ref{Alg1} and justifies this second algorithm.  As before, we assume
that $B_1$ and $B_2$ are large enough that simulation error can be ignored.

\begin{theorem}\label{T2}
  Under Assumptions~\ref{A1} and~\ref{A2},
  \begin{gather*}
    \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V'(h,b) \to^p 1
  \intertext{and}
    \sup_{x}
    \Big\rvert \Pr^*[\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^* \leq x ]
    - \Pr[\hat\tau(h) - \Delta^*(h,b) - \tau \leq x] \Big\lvert \to^p 0.
  \end{gather*}
\end{theorem}

@@

Define the following additional notation:
$r_p(x) = (1,\ x,\dots,\ x^p)'$,
\begin{align}
  \label{eq:5}
  \Bf_+(h)
  & = (1\ \  0)\ \Big(\ssum[+]{i}{h} r_1(X_i/h) r_1(X_i/h)' \Big)^{-1}
    \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
  \label{eq:6}
  \Bf_-(h)
  & = (1\ \ 0)\ \Big(\ssum[-]{i}{h} r_1(X_i/h) r_1(X_i/h)' \Big)^{-1}
    \ssum[-]{i}{h} r_1(X_i/h) \; X_i^2 / h^2.
\end{align}

\subsection{Proof of Theorem~\ref{T1}}
We have
\begin{equation*}
  \hat\tau(h) - \Delta^*(h,b) - \tau = (\hat\tau(h) - \E \hat \tau(h)) +
  (\E \hat \tau(h) - \tau) - (\E^* \hat \tau^*(h) - \tau^*).
\end{equation*}
The design of the bootstrap ensures that
\begin{align*}
  \E^* \hat\mu_{+}^*(h) - \mu_{+}^{*}
  &= h^{2} \mu_+^{*(2)} \Bf_{+}(h)/2,
  &\E^* \hat\mu_{-}^*(h) - \mu_{-}^{*}
  &= h^{2} \mu_-^{*(2)} \Bf_{-}(h)/2,
\end{align*}
almost surely, implying that
\begin{equation*}
    \E^* \hat\tau^*(h) - \tau^{*} = h^2\, \mu_+^{*(2)} \Bf_+(h)/2
      - h^2\, \mu_{-}^{*(2)} \Bf_{-}(h)/2.
\end{equation*}
Combining this result with CCT's Lemma A1, gives
\begin{align}
  \hat\tau(h) - & \E \hat\tau(h) + (\E \hat\tau(h) - \tau) - (\E^* \hat\tau^*(h) - \tau^*)\notag \\
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h) / 2 \big) + O_p(h^{3}) \notag \\
  \label{eq:7}
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 (\hat\mu_-^{(2)}(b) - \mu_-^{(2)}) \Bf_{-}(h) /2 \\
  \notag
  &\pushright{- h^2 (\hat\mu_+^{(2)}(b) - \mu_+^{(2)}) \Bf_{+}(h) / 2 + O_p(h^{3})}
\end{align}
The second equality holds because
$\mu_+^{*(2)} = \hat\mu_{+}^{(2)}(b)$ and
$\mu_-^{*(2)} = \hat\mu_{-}^{(2)}(b)$ almost surely. Asymptotic
normality then follows from normality of $\hat\tau(h) - \E\hat\tau(h)$,
$\hat\mu_+^{(2)}(b) - \mu_+^{(2)}$, and
$\hat\mu_-^{(2)}(b) - \mu_-^{(2)}$ using similar arguments to
CCT's Lemma SA4.D.\qed
